---
title: "rm_db_name"
author: "Alfredo G Marquez"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{rm_db_name}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `rm_db_name()` function was inspired from having column names prefixed by database names when importing the data into R.

One solution to this problem is to use "`as variable_name`" in you SQL code without giving the table an "`as table_name`" alias. This solution works fine when you have less than a dozen or so fields.  What if you had several hundred?  No one in a job with deadlines would rename every single field.

###  Example

For example, lets say that you have a HIVE table called fiscal_dates with 3 fields, greg_d, wk_end_d, and year.

When you query this table, you would expect this:
```{r}
expected <- tibble::tribble(~greg_d,~wk_end_d,~year)
str(expected)
```

Instead you get this:
```{r}
incorrect <- tibble::tribble(~fiscal_dates.greg_d,~fiscal_dates.wk_end_d,~fiscal_dates.year)
str(incorrect)
```

The database prefix is very inefficient moving forward in any data wrangling and machine learning project.

The `rm_db_name()` will remove the prefix and return a dataframe with the correct or desired column names.  
```{r}
corrected <- RToolShed::rm_db_name(incorrect,"fiscal_dates")
str(corrected)
```


